Pool Model - A unified Mathematical\\ Modelling Framework for Food Science

### 2025-10-31 paper/pool_model.tex
more formatting

And after "difficult times" bacteria, also called viable but non-culturable (VBNC), can continue cell division~\citep{kell_viability_1998}.

@@

    L &\stackrel{\lambda}{\longrightarrow} & G\\
    L &\stackrel{\mu}{\longrightarrow} & D\\
    G &\stackrel{\alpha}{\longrightarrow} & 2G\\
    G &\stackrel{\gamma(t)}{\longrightarrow} & L

@@

The ordinary differential equations for the pool model with environmental-shock based back-flow read:

@@

After the rapid temperature increase, the growth slows down till the bacteria that transitioned back to lag-phase go again to growth pool.

>>>>

And after "difficult times" bacteria can continue cell division~\citep{kell_viability_1998}.

@@

    G &\stackrel{\gamma(t)}{\longrightarrow} L

@@

The ordinary differential equations for the pool model with back-flow then read:

@@

After the rapid temperature increase, the growth slows down till the bacteria that transitioned back to lag-phase migrate back to the growth pool.
